\chapter*{Nomenclature} 
\addcontentsline{toc}{chapter}{Nomenclature} 
\paragraph{E\textsubscript{CM}}
The center-of-mass energy E\textsubscript{CM} is the collision energy of a particle accelerator.
If the particles of the colliding beams have equal masses and energies E, the center-of-mass energy can be calculated to be E\textsubscript{CM} = 2E. Its unit is commonly [\si{\GeV}].
\paragraph{$\bm{\mathcal{L}}$}
The luminosity $\mathcal{L}$ of a particle accelerator is a measure of the amount of collisions that can occur. It is given as the number of collisions per area per time, with the units [\si{\per\centi\meter\squared\per\second}].
\paragraph{N}
Every beam bunch contains a certain number of particles, N. This quantity is often called ``bunch population''.
\paragraph{n\textsubscript{b}}
The number of bunches per train or pulse of an accelerator is given as n\textsubscript{b}.
\paragraph{Occupancy}
The detector occupancy is the fraction of detector pixels that are hit by particles with respect to the total number of pixels.
\paragraph{q\textsubscript{b}}
From the number of particles in a beam bunch and their charge, the bunch charge can be calculated in units of Coulomb.
\paragraph{$\bm\sigma$}
$\sigma_{x,y,z}$ gives the size of a beam bunch in the horizontal, vertical and longitudinal direction. When the beam size is given specifically at the interaction point of the accelerator, $\sigma^*$ is used.
\paragraph{$\Delta$t\textsubscript{b}}
The time between each bunch crossing in a particle accelerator.
\paragraph{X\textsubscript{0}}
The radiation length X\textsubscript{0} is a material specific constant, and is defined in two ways depending on the particle type:
\begin{itemize}
 \item The mean length after which the energy of the electron (or any other charged particle) is reduced to 1/e of the initial energy due to bremsstrahlung.
 \item 7/9 of the mean free path of photons before they pair produce.
\end{itemize}
X\textsubscript{0} is measured in [\si{\gram \per\centi\meter\squared}].
