\pdfoutput=1 % for arXiv to use pdflatex
\documentclass[12pt]{article}

%% The graphicx package provides the includegraphics command.
\usepackage{graphicx}
%% The amssymb package provides various useful mathematical symbols
\usepackage{amsmath}
\usepackage{amssymb}
%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
\usepackage{lineno}
\usepackage{url}
\usepackage{xspace,multicol}
\usepackage{siunitx}
\usepackage{subcaption}
\usepackage{color, colortbl}
\usepackage{units}
\usepackage{ragged2e}
\usepackage{array}
\usepackage{tabularx}
\usepackage{authblk}
\usepackage{heppennames}
\usepackage{feynmp}
\usepackage{libertine}
% \usepackage[libertine]{newtxmath}
\usepackage{textgreek}
\DeclareGraphicsRule{*}{mps}{*}{}

\newcommand{\guineapig}{GuineaPig\xspace}
\newcommand{\sid}{SiD\xspace}
\newcommand{\slic}{\textsc{SLIC}\xspace}
\newcommand{\geant}{\textsc{Geant4}\xspace}
\newcommand{\murm}{%
  \ifmmode
    \mathchoice
        {\hbox{\normalsize\textmu}}
        {\hbox{\normalsize\textmu}}
        {\hbox{\scriptsize\textmu}}
        {\hbox{\tiny\textmu}}%
  \else
    \textmu
  \fi
}
\newcommand{\micron}{\ensuremath{\murm\mathrm{m}\xspace}}

\begin{document}

%% Title, authors and addresses

\title{A Study of the Impact of Muons from the Beam Delivery System on the SiD Performance}

\author{Anne Sch\"utz\footnote{Karlsruhe Institute of Technology (KIT), Department of Physics, Institute of Experimental Nuclear Physics (IEKP), Wolfgang-Gaede-Str. 1, 76131 Karlsruhe, Germany}, Marcel Stanitzki\footnote{Deutsches Elektronen-Synchrotron (DESY), Notkestr. 85, 22607 Hamburg, Germany}}

\maketitle

%%
%% Start line numbering here if you want
%%
\linenumbers

\begin{abstract}
%% Text of abstract
To suppress the muon background arising from the Beam Delivery System (BDS) of the International Linear Collider (ILC), and to hinder it from reaching the interaction region, two different shielding scenarios are under discussion: five cylindrical muon spoilers with or without an additional magnetized shielding wall.
Due to cost and safety issues, the case preferred by the MDI group is to omit the shielding wall, which on the other hand brings other disadvantages.
To support the decision making, the impact of the muons from the two different shielding scenarios was studied in a full Geant4 detector simulation of the SiD detector, one of two proposed detectors for the ILC. 
Input to this study is the muon background created by the beam traveling through the BDS, which was simulated with the simulation tool MUCARLO.
\end{abstract}


%% main text
\section{Introduction}
\label{sec:introduction}

Although much more forgiving than for LHC collisions, activity generated by ILC collisions still needs to be considered in the geometric and readout design of SiD detector components, particularly those closest to the beamline. In this study, we have considered the impact of ILC beam-beam collision activity on the pixelization (spatial and temporal) of the pixel vertex detector (VXD), the readout architecture of the electromagnetic calorimeter (ECAL), and the geometry and layout of the Beamline Calorimeter (BeamCal). We have also considered the impact of the longitudinal position of the BeamCal (tied to the value of $L^*$, the distance from the interaction point to the tip of the final focusing quadrupole), and the inclusion of a dedicated magnetic field from an anti-detector-integrated dipole (anti-DiD), intended to sweep beam-beam collision products into the ILC beam exit pipe, on the backgrounds that populate these innermost detector elements.

As currently envisioned, the ILC machine will deliver beam trains at a rate of \unit[5]{Hz}. Three sets of possible beam parameters, as defined in the Technical Design Report~\cite{TDR}, are listed in Table~\ref{tab:ILC_parameters}. At the center-of-momentum energy \mbox{$E_\text{CM} = \unit[500]{GeV}$}, in the energy region for which the ILC would be expected to run in its first years of operation, two sets of parameters are presented. For the baseline (lower luminosity) set, each train would consist of 1312 crossings each separated by \unit[554]{ns}, for a total train duration of 0.72 ms, and with an integrated luminosity of \unit[3.6]{nb$^{-1}$} per train. A higher-luminosity \unit[500]{GeV} scenario envisions a train of 2625 bunches each separated by \unit[366]{ns}, with total train duration of \unit[0.96]{ms} and an integrated luminosity if \unit[7.2]{nb$^{-1}$} per train. A third set of parameters, proposed for running at an upgraded center-of-momentum energy of \unit[1]{TeV}, was not considered in this study. In all cases, though, the interval of \unit[199]{ms} between successive trains can be made use of for digital processing of analog signal pulses. Design considerations due to high cross-section background processes arise both from the effect of individual crossings, as well as from the effect of multiple beam crossings integrated over portions of the, or the entire, beam train.

\include{MUCARLO}
\include{MuonSiD}
\include{Conclusions}


\section*{Acknowledgments}
Grateful acknowledgments to Lewis Keller and Glen White from SLAC for the simulation of the muons from the BDS and their big support.

\include{Appendix}

%% References with bibTeX database:

\bibliographystyle{abbrv}
%\bibliographystyle{model1-num-names} %Doesn't work well if you also cite webpages (Confluence page)
\bibliography{PairBackground_in_SiD.bib}

\end{document}
